Experiment 1 of 4

### 2016-09-25 experiments/e1/writeup/e1.Rmd
recompiled unsaved digit changes

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(
    summary(
    ac.lmer.1
    )$coefficients,
    digits=c(0, 2, 2, 2, 5), 
    caption="Error rates model"),
  caption.placement="top", type='html')
```

>>>>

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(
    summary(
    ac.lmer.1
    )$coefficients,
    digits=c(0, 2, 2, 2, 7), 
    caption="Error rates model"),
  caption.placement="top", type='html')
```
